---
title: "Homework 1"
author: "Laura Brubaker-Wittman"
date: "9/12/2019"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE, error = TRUE)
```

# R Markdown
## Module 4: Challenge 1

**Directions:** *First, create a vector of 1 word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”*

For this, I made a vector with each of the words in the sentence as a different element:
``` {r ulysses <- c("Stately", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")}
ulysses
```
Since when I knit to html I am getting an error for some reason, even though it is showing in my workspace (will put that as one of my biggest challenges), here is what my code looks like (also, if you open on this in R studio and not html, you should be able to see the code chunk and run it to see that it works:

ulysses <- c("Stately", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")
ulysses

[1] "Stately"   "plump"     "Buck"      "Mulligan"  "came"      "from"      "the"       "stairhead" "bearing"  
[10] "a"         "bowl"      "of"        "lather"    "on"        "which"     "a"         "mirror"    "and"      
[19] "a"         "razor"     "lay"       "crossed"  

**Directions, continued:** *Then, extract every third element of this vector.*

While I did read the hints, because I had already written the string as separate characters and R Studio showed me that it was a 22 element vector in the "values" section of the "Environment" tab, I simply asked wrote a command to bring up every third element manually:

```{r ulysses_third_word <- c(3, 6, 9, 12, 15, 18, 21)}
ulysses[ulysses_third_word]
```
More errors in the Rmarkdown html, but here is what it looks like in the workspace on R studio:

ulysses_third_word <- c(3, 6, 9, 12, 15, 18, 21)

ulysses[ulysses_third_word]

[1] "Buck"    "from"    "bearing" "of"      "which"   "and"     "lay"   

I am guessing there are more efficient ways to do this, but hey, this worked!

## Module 4: Challenge 2

**Directions:** *Using this matrix (again errors, and sorry the written out one looks so awful:*

```{r m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)}
m
```

m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)

m

[,1] [,2] [,3] [,4] [,5] [,6] [,7] [,8] [,9] [,10]

[1,]    1    9   17   25   33   41   49   57   65    73

[2,]    2   10   18   26   34   42   50   58   66    74

[3,]    3   11   19   27   35   43   51   59   67    75

[4,]    4   12   20   28   36   44   52   60   68    76

[5,]    5   13   21   29   37   45   53   61   69    77

[6,]    6   14   22   30   38   46   54   62   70    78

[7,]    7   15   23   31   39   47   55   63   71    79

[8,]    8   16   24   32   40   48   56   64   72    80

**Directions, continued:** *Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x*