---
title: "AN597_Week2"
author: "Christian Gagnon"
date: "9/11/2019"
output: html_document
---

hi!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Module 4


##Challenge 1
Input data into R.
```{r}
u <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
u
```
Remove punctuations.
```{r}
v <- gsub("[[:punct:]]","",u)
v
```
Split my string into substrings.
```{r}
w <- strsplit(v," ")[[1]]
w
```
Formating my string into a matrix where each word is a seperate row.
```{r}
z<-matrix(w, nrow = 22 , ncol = 1)
z
```

Obtaining every 3rd character by specifying every 3rd row.
```{r}
z[c(3,6,9,12,15,18,21)]
```



##Challenge 2

This is the matrix we are given:
```{r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE,)
m
```

Create 2 vectors which we can then bind together to end up with columns 2,3, and 6.
```{r}
x1<-m[1:8,2:3]
x1
x2<-m[1:8,6]
x2
x<-cbind(x1,x2)
x
```

This gives us all of rows 6 through 9:
```{r}
x<-m[6:8,1:9]
x
```

This gives us from row 2, column 2 to row 6, column 9:
```{r}
m
x<-m[2:6,2:9]
x
```

##Challenge 3

Creating an array with the number 400 to 1 in decending order and dimensions of 5x5x4x4:
```{r}
a<-array(data=400:1, dim=c(5,5,4,4))
a
```

follow up questions (What do these return):
```{r}
a[1, 1, 1, 2]
```

```{r}
a[2, 3, 2, ]
```

```{r}
a[1:5, 1:5, 3, 3]
```

#Challenge 4
This one is hard, I'm not sure if this is what he is looking for:
```{r}
a<-list("Primates",
        "Haplorhini",
        "Anthropoidea",
        "Platyrrhini",
        c("Cebidae","Atelidae","Pitheciidae"),
        "Catarrhini",
        c("Cercopithecidae","Hylobatidae","Hominidae"),
        "Tarsioidea",
        "Tarsiidae",
        "Strepsirhini",
        "Lorisoidea",
        c("Lorisidae","Galagidae"),
        "Lemuroidea",
        c("Cheirogaleidae","Lepilemuridae","Indriidae","Lemuridae","Daubentoniidae"))
a
```

Create the 5x3 matrix ordered by row using the provided number
```{r}
b<-matrix(c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2),nrow=5,ncol=3,byrow=TRUE)
b
```

Coerce into a data frame:
```{r}
df <- data.frame(b)
df
```

Convert column 2 to logical and column 3 to factor
```{r}
as.logical(df$X2)
as.factor(df$X3)
str(df)

```

Hi Christian-

Looking at your code and the html rendered from RMarkdown, everything in here looks pretty good! Seeing how you did a few things actually helped me see where I might be having a few issues myself. Thanks! It also looked like on the things we did similarly, we got the same answers. I like the list you did for the Primates question, and it looks like all three of us in our group did it a but differently, so I think this will be a good one to ask Chris as far as what he actually had in mind for us to do, or if there is some interesting command as far as making nested lists that we could learn? Honestly, that is all I have for you, but please let me know if you have specific questions! If you write down your five challenges next time, your peer group person can comment on those directly! 

Laura